\documentclass[myletter, a4paper, 11pt]{scrlttr2}

\begin{document}

\begin{letter}{
    Elisa Ferracane\\
    Research Scientist\\
    Abridge
}

\setkomavar{subject}{Application for NLP Research Intern}

\opening{Dear Elisa,}

I am a 4th year Ph.D candidate in the Department of Linguistics at The University of Texas at Austin, advised by Dr. Jessy Li and Dr. David Beaver. My research focuses on studying interpersonal biases in language use among online communities. Specifically I'm focusing on whether these biases manifest through subtle systematic variations in semantic and pragmatic attributes of words and sentences. Previously, I have studied how individuals perform pragmatic acts online (like giving advice), as well as the diversity of generalizations available across different predicate-argument structures, both of which inform my research work now.\\

I am keenly interested in an internship at Abridge for the people, and for the research and engineering that flows into the company's product. I would cherish the opportunity to work with a small team focused on building a great product, and exploring how my unique skills can help strengthen it. My goal for a summer internship at Abridge is to use my experience with language variation and generalization to work on a project that can improve core products and technologies at the company like structured summarization, ultimately leading to a publishable paper. For instance, your research paper `Towards Fairness in Classifying Medical Conversations into SOAP Sections' describes one such type of problem that I would love to work on --- what is the nature of language variation in the data, and how does it affect model performance? How can we make models robust to such variation? If models need to be updated to handle a change in the incoming data distribution, can we use unsupervised methods to inform model update schedules? If accepted for this internship, I would be very excited to work on these sorts of problems.\\

Thank you for your time, and I look forward to talking with you about your views and goals for a research internship at Abridge.

\setkomavar{fromname}{Venkata S Govindarajan}
\closing{Sincerely,}

% \encl{Résumé}

\end{letter}

\end{document}
