\smallentry
  {\large \href{https://nasslli25-nlp-css.github.io}{NASSLLI summer course}}{\large Summer 2025}{I designed and taught a week-long summer course on Natural Language Processing \& Computational Social Science (CSS) with my colleague \href{https://www.laurabiester.com}{Laura Biester} at \href{https://nasslli25.shane.st}{NASSLLI 2025}, held at University of Washington, Seattle. The course focused on bridging theoretical concepts and engineering principles in NLP towards writing research papers in CSS, using insights from our past papers.}

\smallentry
  {\large Tech Innovation Summer Academy (TISA)}{\large Summer 2025}{TISA is a one-week summer program that introduces students to computer science with a focus on understanding through building applications and tools. I served on the organizing committee helping with planning and organization, and designed course materials for sessions on Machine Learning and Artificial Intelligence.}

\smallentry
  {\large \href{https://sites.google.com/utexas.edu/sxsw/archive}{South by Semantics Workshop}}{\large 2022--24}{I co-organized a series of talks on semantics, computation and philosophy of language. Our goal was to provide a forum for emerging scholars with UT Austin's rich community of language researchers, and to foster collaboration and dialogue through social events organized with the talks.}
  
\smallentry
    {\large \href{http://tls.ling.utexas.edu/}{Texas Linguistics Society} (TLS) Conference}{\large 2021--22}{TLS is an annual student-run academic conference by the Department of Linguistics at UT Austin which includes presentations in all areas of linguistics. I served on the organizing committee and was involved in reviewing and assigning submissions for review, website design, scheduling, logistics for a fully virtual conference, and chairing keynote sessions and talks.}

\leftskip0em\relax

\subsection{Reviewer}

\quad ACL ARR 2023--present, EMNLP 2023--24, ACL 2023, *SEM 2023--25, SIGDIAL 2022--23

\subsection{Volunteer}

\quad \href{http://underpaidatut.org}{Underpaid\makeatletter @\makeatother UT} (2023-24)
